### 2012-05-19 GUIErrorDetector/paper/evaluation.tex
Small tweaks.  Also adjust spacing to avoid bad page breaks.

\item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions using mutlithreaded execution.

@@

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without our enhancements
(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they do not scale to our subject programs.

Subject SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
Two subjects (MyTracks and Fennec)
use a customized pattern to interact with the GUI framework.
For them, we added \filternum user-defined filters, described in Section~\ref{sec:heuristic}.
In this experiment, none of the paper
authors was familiar with the subjects, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error S3dropbox has been confirmed, and we have reproduced other errors.
All found bugs and our experimental results are
publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
%in which 2 errors in FileBunker and ArecaBackup
%have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.

@@

We found GUI developers have already
used design patterns, runtime checks, and testing to avoid violating
the single-GUI-thread rule. However, due to the huge space of
possible UI interactions, hard-to-find
invalid thread access errors still exist.
%Thus, a static analysis as presented in this paper
%would be useful.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths
on average, but did not output any real errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15. Thus, a rough estimation for the number of distinct
non-cyclic paths gives an astronomically large number: 
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subjects with \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for the JVM), running Windows 7.
For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
within 252 seconds using the most expensive 1-CFA call graph construction
algorithm. Analyzing other subjects or using different algorithms took less time.
Call graph construction took 33--91\% of the total time.

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in three aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, like many bug-finding techniques, our technique
is neither sound nor complete. It may issue false positives
due to the conservative nature of a static analysis.
It may miss true positives due to the graph search strategy,
and it never reports cyclic paths. Furthermore, for the
sake of scalability, our tool implementation uses the default
configuration of WALA and ignores part of the AWT library. Thus,
it missed one error in S3dropbox which can be found by using a different
technique~\cite{JSR308-webpage-201110}.
Designing better call graph construction algorithms,
graph search strategies, and filtering heuristics may alleviate this limitation.
Third, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.

>>>>

\item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions using multithreaded execution.

@@

We ran our tool on each subject program with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without our enhancements
(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they do not scale to our subject programs.

Subject SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
Two subjects (MyTracks and Fennec)
use a customized pattern to interact with the GUI framework.
For them, we added \filternum user-defined filters, described in Section~\ref{sec:heuristic}.
In this experiment, none of the paper
authors was familiar with the subject programs, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error in S3dropbox has been confirmed, and we have reproduced all the other errors.
All found bugs and our experimental results are
publicly available at \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
%in which 2 errors in FileBunker and ArecaBackup
%have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.

@@

\enlargethispage{5pt}

We found that GUI developers have already
used design patterns, runtime checks, and testing to avoid violating
the single-GUI-thread rule. However, due to the huge space of
possible UI interactions, hard-to-find
invalid thread access errors still exist.
%Thus, a static analysis as presented in this paper
%would be useful.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject program for 1 hour.  It explored 5.1$\times$$10^9$ paths
on average, but did not output any of the 10 errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15.  The number of distinct
non-cyclic paths is astronomically large; a rough estimate is
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subject programs with \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for the JVM), running Windows 7.
For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
within 252 seconds using the most expensive 1-CFA call graph construction
algorithm. Analyzing other subjects or using different algorithms took less time.
Call graph construction took 33--91\% of the total time.

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in three aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, like many bug-finding techniques, our technique
is neither sound nor complete. It may issue false positives
due to the conservative nature of a static analysis.
It may miss true positives due to the graph search strategy,
and it never reports cyclic paths. Furthermore, for the
sake of scalability, our tool implementation uses the default
configuration of WALA and ignores part of the AWT library. Thus,
it missed one error in S3dropbox which we later found by using pluggable type-checking~\cite{DietlDEMS2011}.
Designing better call graph construction algorithms,
graph search strategies, and filtering heuristics may alleviate this limitation.
Third, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.
